Paper_analyses

### 2021-08-03 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground))

@@

tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground / 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))

@@

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, ArousalMean))+
  # geom_point()+
  # stat_summary(geom = 'pointrange')
 geom_boxplot()
tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, arousal_rel_neutral_ground_z ))+
  # geom_point()+
  geom_boxplot()
  # stat_summary(geom = 'pointrange')
```

>>>>

# same with self report

tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_self <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal - tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal_self,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal - 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal_self, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal - mean(tmp.df4_full_stim_downs_jun2021_60bins$arousal, na.rm = TRUE)))

# visualise new ground and self report arousal baseline separetelly for positive and negative valenced stimuli (based on IAPS validation)
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground))

@@

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, arousal_rel_neutral_self))+
  geom_point()+
  stat_summary(geom = 'pointrange')

arousal_rel_neutral_self
```
```{r}
# create the new arousal corrected within positive/negative - neutral
tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground / 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))

# do the same with self report arousal but using ground valence?
tmp.df4_full_stim_downs_jun2021_60bins$arousal_self_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                                     tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground / 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))

@@

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, ArousalMean))+
  # geom_point()+
  # stat_summary(geom = 'pointrange')
 geom_boxplot()
tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, arousal_rel_neutral_ground_z ))+
  # geom_point()+
  geom_boxplot()
  # stat_summary(geom = 'pointrange')

# original valence arousal
tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ValenceMean, ArousalMean ))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ValenceMean, arousal_rel_neutral_ground_z ))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()
